---
title: "R_excercise"
output: html_document
date: "2023-05-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(readr)
options(repr.plot.width = 6, repr.plot.height = 6)
```

## Read iris data

```{r}
Iris <- read.csv('./Iris.csv')
class(Iris)
```

## Let's look at the iris data \# we do this by looking at the first five columns

```{r}
head(Iris)
```

# Scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors

```{r}
ggplot(Iris, aes(x = SepalLengthCm, y = SepalWidthCm, color = Species)) +
  geom_point() +
  labs(x = "Sepal Length in cm ", y = "Sepal Width in cm")
```

## Add regression line for the previous plot with the whole dataset (regardless of the species)

The argument aes(group = 1) in the geom_smooth() function is used to indicate that all data points in the dataset should be considered as a single group when performing the regression.

### Linear model

```{r}
ggplot(Iris, aes(x = SepalLengthCm, y = SepalWidthCm)) +
  geom_point(aes(color = Species, group = Species)) +
  geom_smooth(method = lm, se = FALSE, aes(group = 1)) +
  labs(x = "Sepal Length in cm", y = "Sepal Width in cm")
```

### Method auto

```{r}
ggplot(Iris, aes(x = SepalLengthCm, y = SepalWidthCm)) +
  geom_point(aes(color = Species, group = Species)) +
  geom_smooth(method = 'auto', se = FALSE, aes(group = 1)) +
  labs(x = "Sepal Length in cm", y = "Sepal Width in cm")
```

## Pearson correlation

```{r}
cor(iris$Sepal.Length, iris$Sepal.Width)
```

Since the correlation coefficient is negative and close to zero, it indicates a weak, negative correlation between sepal length and sepal width in the data set.

## Make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors

```{r}
ggplot(Iris, aes(x = Species, y = PetalWidthCm, fill = Species)) +
  geom_boxplot() +
  labs(x = "Species", y = "Petal Width in cm", title = "Boxplot of Petal Width by Species") +
  scale_fill_manual(values = c("#F8766D", "#00BA38", "#619CFF"))
```

## Make the histogram for Petal.Width with 3 species separately in x-axis in different colors

```{r}
ggplot(iris, aes(x = Petal.Width, fill = Species)) +
  geom_histogram(position = "identity", bins = 30, alpha = 0.7) +
  labs(x = "Petal Width in cm", y = "Count", title = "Histogram of Petal Width by Species") + 
  scale_fill_manual(values = c("#F8766D", "#00BA38", "#619CFF"))
```

## Run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species

The output of the t.test() function will provide information about the t-statistic, degrees of freedom, the p-value, and whether the difference in means is statistically significant.

```{r}
setosa_width <- iris$Petal.Width[iris$Species == "setosa"]
virginica_width <- iris$Petal.Width[iris$Species == "virginica"]
t_test_result <- t.test(setosa_width, virginica_width)
t_test_result
```

The Welch Two Sample t-test revealed a highly significant difference (t = -42.786, df = 63.123, p \< 2.2e-16) in the mean Petal.Width between the Setosa and Virginica species. These findings provide strong evidence to reject the null hypothesis, indicating a statistically significant distinction in the Petal.Width between the two species. The Setosa species exhibited a mean Petal.Width of 0.246, while the Virginica species had a mean Petal.Width of 2.026. This result highlights the significant variation in Petal.Width, emphasizing its importance as a distinguishing feature between the Setosa and Virginica species.
